%-------------------------
% Resume in LateX
% Author : Pham Thanh Duy
%------------------------

\documentclass[letterpaper,10pt]{article}

% ------------------- PACKAGES -----------------------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{tikz}
\usepackage{helvet}

\input{glyphtounicode}
\renewcommand{\familydefault}{\sfdefault}

% ------------------- PAGE SETUP -----------------------
\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{2pt}\scshape\bfseries\Large\raggedright
}{}{0em}{}[\color{black}\titlerule \vspace{2pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
    \item\small{
        \textbf{#1}{: #2 \vspace{2pt}}
    }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \vspace{5pt}
        \textbf{\LARGE#1} & \normalsize#2 \\
        \vspace{5pt}
        \textbf{\textit{\small#3}} & \textit{\normalsize #4} \\
    \end{tabular*}\vspace{-10pt}
}

\newcommand{\resumeProfile}[2]{
    \begin{center}
        \begin{minipage}[c]\textwidth
            \setlength{\parskip}{5pt}
             \begin{flushleft}
                  \noindent {#1}

                  \vspace{10pt}
                  \noindent {#2}
             \end{flushleft}
         \end{minipage}
    \end{center}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \vspace{5pt}
      \textbf{#1} & #2 \\
      \vspace{5pt}
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*, itemsep=6pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\resumeHeading
    {Pham Thanh Duy} {\href{mailto:thanhduysofeng@gmail.com}thanhduysofeng@gmail.com \textbar{} \href{https://www.linkedin.com/in/tduy-dev}{LinkedIn}}
    {Full-stack Developer} {Mobile: \href{tel:+84869997242}+84-869997242}


%-----------PROFILE-----------------
\section{profile}
\resumeProfile
    {I am a Full-Stack Developer with over 4 years of experience in building and maintaining large-scale software systems. Specialized in Microservices architecture, Cloud technologies, and the Java/Spring ecosystem.}
    {Proven ability to deliver scalable and optimized solutions, performing root cause analysis, and quickly adapt to new technologies to address complex technical challenges.}


%--------SKILLS------------
\section{skills}\vspace{-4pt}
    \resumeSubHeadingListStart
        \resumeSubItem{Programing Languages}
            {Java, JavaScript, TypeScript, HTML5, CSS3}
        \resumeSubItem{Framework}
            {Spring Boot, Spring Security, ReactJS, VueJS, NodeJS}
        \resumeSubItem{Technologies}
            {SQL (MySQL, SQL Server), MongoDB, Redis, Elasticsearch, Kafka, Docker, AWS (EC2, S3, Lambda)}
        \resumeSubItem{Engineering Practices}
            {Microservices, REST/gRPC, Mockito (Unit Testing), GitHub/GitLab (CI/CD), SonarQube (Code Quality),...}
        \resumeSubItem{Soft Skills}
            {Project Management, Problem Solving, Critical Thinking, Teamwork, Adaptability, Time Management}
    \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{experience}\vspace{-4pt}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Code88 Company}{Ho Chi Minh city}
            {Middle Software Engineer}{Spring 2021 -- Present}
        \resumeItemListStart
            \resumeItem{Building Application Structure}
                {Create an admin web application (ReactJS) designed to manage customers registered through the agency, rather than on the website themself. The system provides settings for daily player management and reporting.}
            \resumeItem{State Management Optimization}
                {Implemented efficient front-end state management strategy using React’s Context API and memoization (useState, useMemo, useCallback,...) to avoid unnecessary re-renders. Improved rendering performance by over 40\% in complex components dealing with large datasets. Applied lazy loading and data normalization techniques to optimize data flow and responsiveness.}
            \resumeItem{System Architecture and Migration}
                {Responsible for migrating the system from Java 8 to Java 17, and refactoring the architecture from a Monolithic architecture (Spring MVC) to Microservices (Spring Boot) to make the system more flexible and easier to maintain.}
            \resumeItem{Application Security}
                {Developed and integrated secure RESTful APIs using Spring Security and JWT to protect critical resources and ensure secure user authentication and authorization.}
            \resumeItem{High-Volume Data Processing}
                {Engineered a multithreaded solution to export over 1 million records to Excel, storing the output in AWS S3 to optimize performance and prevent out-of-memory issues.}
            \resumeItem{Asynchronous Communication}
                {Designed and implemented a decoupled email delivery service using Kafka, streamlining communication workflows and reducing load on the core services.}
            \resumeItem{Caching Strategy}
                {Integrated Redis for efficient cache management, significantly reducing database load and improving response times for frequently accessed data.}
            \resumeItem{Logging and Monitoring}
                {Developed an AOP-based logging system for comprehensive application monitoring, supporting rapid debugging and incident resolution.}
            \resumeItem{API Documentation Automation}
                {Develop an API documentation file management solution to automate Swagger/OpenAPI generation from endpoint description documents, supporting a rapid and standardized development process.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{education}\vspace{-4pt}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Industrial University of HCM city}{}
            {Software Engineer}{Sep 2016 -- Oct 2020}
    \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}